Waiting time analysis

### 2025-05-23 notebooks/02_waiting_time.qmd
chore: cleanup

>>>>

## Old codes

```julia
subset_jno(df, r) = subset(df, :radial_distance => x -> round_c.(x) .== r)
subset_time(df, t) = subset(df, :time => x -> x .< t)

bin(x, bin_size) = @. round(x / bin_size) * bin_size
bin(bin_size) = x -> bin(x, bin_size)

df = wind_df;
df_s1 = subset(df, :time => t -> year.(t) .== 2013);
df_s2 = subset(df_s1, :time => t -> month.(t) .< 2);

jno_df_s1 = subset(jno_df, :time => t -> year.(t) .== 2011);
jno_df_s2 = subset(jno_df, :time => t -> year.(t) .== 2016);

jno_ρ_df = @chain jno_df begin
    @transform!(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
    )
end;

time_interval = Day(160)

jno_ρ_df = @chain jno_df begin
    @transform(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
        :l = :L_k .* (abs ∘ cosd).(:θ_vn),
        :l_n = :L_k .* (abs ∘ cos ∘ atan).(:Vn_y ./ :Vn_x)
    )
    @transform(
        :l_ratio = :l ./ :r,
        :l_n_ratio = :l_n ./ :r
    )
    groupby(:time_bin)
    combine(
        nrow,
        :time => get_wt_fit_params => :τ,
        [:r :l :l_ratio :l_n_ratio] .=> mean
    )
    # subset(:nrow => x -> x .> 2000)
    @transform(
        :ρ = 1 ./ :τ,
    )
    @transform(
        :ρ_l = :ρ ./ :l_ratio_mean * maximum(:l_ratio_mean),
    )
    sort(:r_mean)
end

wind_ρ_df = @chain wind_df begin
    @transform!(
        :time_bin = (:time - minimum(:time)) ./ time_interval .|> round,
    )
    groupby(:time_bin)
    combine(
        nrow,
        :time => get_wt_fit_params => :τ,
    )
    @transform!(
        :ρ = 1 ./ :τ,
    )
end

df = leftjoin(jno_ρ_df, wind_ρ_df, on=:time_bin, makeunique=true)
df.ρ_ratio = @. df.ρ / df.ρ_1

x = :time_bin => "Time"
legends = ["Juno", "Wind"]
specs = data(df) * mapping(x, [:ρ_l, :ρ_1] .=> "Normalized Occurence rates") * mapping(color=dims(1) => renamer(legends))
draw(specs)
easy_save("ocr/ocr_normalized_by_r")

x = :r_mean => r_lab
specs = data(df) * mapping(x, :ρ)
draw(specs)

y = [:ratio_n, :ratio]
specs = data(df) * mapping(x) * mapping(y, color=dims(1) => renamer(string.(y)))
plt2 = draw(specs)
```
